Notes on Semi-Supervised `Novelty Detection'

### 2011-04-28 semisupervised/notes.tex
more notes

\subsubsection{Modeling the World with Graphical Models}
The previous experiences assume perfect knowledge on the probability distributions functions.
This sections presents how Dora models those distributions and how to perform
novelty detection with them.

Dora uses \emph{probabilistic graphical models} to represent all extracted knowledge from the world.
Those allow to easily model certain probabilistic properties such as conditional independence.
And easy the process of several computational problems on the distributions.
Several tools exists for this type of graphical manipulation such as: \emph{Bayesian networks}, \emph{Markov Random Fields}
or \emph{Factor Graphs}.

Dora underlying graphical methods are based on \emph{Factor Graphs}\citep{kschischang2001factor}, which are bipartites graph composed of variable and factor nodes representing the random variables and several factor functions between the variables that are used to decomposed the distribution.

\begin{figure}
Graphical model of Dora
\end{figure}

We will use $P(G)$.

We will try to 
In this section, I should describe how we use graphical models to model both $P(x|k)$ and $P(x)$.
And made them as $P(G)$ and $P(G')$.

>>>>

\clearpage
\subsection{Modeling the World with Graphical Models}
The previous experiences assume perfect knowledge on the probability distributions functions.
This sections presents how Dora models those distributions and how to perform novelty detection with them.

Dora uses \emph{probabilistic graphical models} to represent all extracted knowledge from the world.
Those allow to easily model certain probabilistic properties such as conditional independence
and easy the process of several computational problems on the distributions.
Several tools exists for this type of graphical manipulation such as: \emph{Bayesian networks}, \emph{Markov Random Fields}
or \emph{Factor Graphs}.

Dora underlying graphical methods are based on \emph{Factor Graphs}\citep{kschischang2001factor}: bipartites graphs composed of variable and factor nodes representing the random variables and several factor functions between the variables that are used to decomposed the distribution.

\begin{figure}[h]
\begin{tikzpicture}
\node[circle,fill=blue!20] (room1) {Room};
\node[circle,fill=blue!20] (Appearance) {Apperance};
\end{tikzpicture}
\caption{Example of a factor graph used for Dora.}
\end{figure}

At any moment dora has a graph $G$ representing a set of random variables the system is aware of and all the probabilistic connections between them.
The observed values are set by the sensed properties and inferences can be done on the remaining ones.

Assuming the graph edges capture the properties of the distribution $P(x|known)$.
$G$ becomes indeed our replacement for that distribution and so $P(x|known) = P(x|G)$.

In order to generate a simple and interesting properties we decided to model $P(x)$ also with a graphical model.

Evaluating $P(x|G)/P(x|G')$...

Method:
\begin{enumerate}
\item Train a graph model for unlabelled data without the labelled variables.
\item Add the labelled variables and train the factors with the labelled data.
\item Use $P(x|G)$ as novelty threshold.
\end{enumerate}
